---
title: "ggplot time hw"
output: html_document
---


```{r libraries and functions}
library(ggplot2)
library(rwunderground) 
# api for weather data, obtain API from https://www.wunderground.com/weather/api/d/pricing.html
# use Anvil Plan as developer (register as new member); use set_api_key and forecast10day
# also use devtools::install_github("ALShum/rwunderground") see https://github.com/alshum/rwunderground
library(lubridate)     # tidyverse package for date manipulation (using function mdy)
library(quantmod)      # includes zoo (masks as.Date from base R), xts; used for getSymbols 
library(scales)        # For axis date formatting via labels
library(broom)         # use function tidy to create data frame from lists
library(tidyr)         # tidyverse package for data frame/tibble manipulation (using function spread)
library(dplyr)         # Used for filter
library(blscrapeR)     # retrieve Bureau of Labors stats via bls_api function

# Custom function used to format axes labels with degree sign for temperatures
add_degree <- function(x) {
  paste(x, " degrees",sep = "")
} 

# key for API call to weather underground via the rwunderground package. Can set the api key in the call, in advance via "set_api_key" or set in .Renviron file by adding WUNDERGROUNDID = "api key"
set_api_key("d29f1ed9ec678880")

```



Problem 1) Using the rwunderground package (you will need to request an api key per the instructions in the lecture), display a graph as provided in the PowerPoint showing the difference between the high and low temperatures for Dallas, Texas for each day (note: the actual dates can vary since the forecast of ten days varies by when the homework is completed).
```{r dates with weather via API}

ten_day_DFW_forecast = forecast10day(set_location(territory = "Texas", city = "Dallas"))

forecast.p <- ggplot(ten_day_DFW_forecast, aes(x = date))
forecast.p  + 
  geom_line(aes(y = temp_high), color = 'coral1') + 
  geom_line(aes(y = temp_low), color = 'cyan1') +
  scale_y_continuous(name = 'Temperatures', labels = add_degree) + 
  theme(axis.text.y=element_text(angle = 45, hjust=1)) + # call custom function to add degree symbol
  
  scale_x_datetime(name = 'Dates', labels = date_format("%b/%d/%y")) + 
  theme(axis.text.x=element_text(angle = 270, hjust=0))  
# Rotate x axis labels to avoid overlap
# Date formatting legend
#   %B = month name
#   %Y = four digit year
#   %m = month #
#   %y = two digit year
#  %b = abbreviated month name

```

Problem 2) We will project the stock prices for AT&T (T symbol) and Toyota (TM symbol) via the quantmod package (using the same function as in the lecture). Read stock data for AT&T and Toyota for dates from January 1 to September 30 2017. Create a plot using ggplot identical to the graph provided in the PowerPoint, with AT&T Graph the AT&T and Toyota open prices over the data ranges of January 1 2017 to December 31 2020. Using smooth geoms with a regular linear model, project the prices through the entire date range of the graph.
```{r stock data and exponential growth}


stock_data <- getSymbols(c("T","TM"),src='yahoo', from = "2017-01-01", to = "2017-09-30")
#head(stock_data)
#str(T) # xts object
#str(TM) # xts object

# quantmod creates xts object for each symbol provided
ATT_Stock <- fortify(T) # fortify ggplot2 function that converts xts to usable data frame (old solution)
#head(ATT_Stock)

# quantmod creates xts object for each symbol provided
Toyota_Stock <- fortify(TM) # fortify ggplot2 function that converts xts to usable data frame (old solution)
#head(Toyota_Stock)


ggplot() + 
  geom_line(data = Toyota_Stock, aes(x = Index, y = TM.Open), color = 'coral1') +
  geom_smooth(data = Toyota_Stock, aes(x = Index,y = TM.Open), color = "coral1", method = "lm", fullrange = TRUE) + 
  geom_line(data = ATT_Stock, aes(x = Index, y = T.Open), color = 'cyan1') +
  geom_smooth(data = ATT_Stock, aes(x = Index, y = T.Open), color = "coral1", method = "lm", fullrange = TRUE) +
  scale_x_date(name = "Dates", limits = c(as.Date("2017-01-01"), as.Date("2020-12-31"))) + 
  scale_y_continuous(name = "Open", labels = comma, limits = c(10,125))

ggsave("stock data going till sep 30.png")


################################################################################################

stock_data <- getSymbols(c("T","TM"),src='yahoo', from = "2017-01-01", to = "2017-10-09")
#head(stock_data)
#str(T) # xts object
#str(TM) # xts object

# quantmod creates xts object for each symbol provided
ATT_Stock <- fortify(T) # fortify ggplot2 function that converts xts to usable data frame (old solution)
#head(ATT_Stock)

# quantmod creates xts object for each symbol provided
Toyota_Stock <- fortify(TM) # fortify ggplot2 function that converts xts to usable data frame (old solution)
#head(Toyota_Stock)



ggplot() + 
  geom_line(data = Toyota_Stock, aes(x = Index, y = TM.Open), color = 'coral1') +
  geom_smooth(data = Toyota_Stock, aes(x = Index,y = TM.Open), color = "coral1", method = "lm", fullrange = TRUE) + 
  geom_line(data = ATT_Stock, aes(x = Index, y = T.Open), color = 'cyan1') +
  geom_smooth(data = ATT_Stock, aes(x = Index, y = T.Open), color = "coral1", method = "lm", fullrange = TRUE) +
  scale_x_date(name = "Dates", limits = c(as.Date("2017-01-01"), as.Date("2020-12-31"))) + 
  scale_y_continuous(name = "Open", labels = comma, limits = c(10,125))

ggsave("stock data going till oct 10.png")

```
